
```{r load packages}
# INSTALL AND LOAD PACKAGES ################################

library(datasets)  # Load base packages manually

# Installs pacman ("package manager") if needed
if (!require("pacman")) install.packages("pacman")

# Use pacman to load add-on packages as desired
pacman::p_load(pacman, rio) 
```

## The Data
The data files analyzed in this project are the scripts of the original StarWars trilogy.

## Questions to be answered.

The focus of the questions will be on the main characters. Specifically Luke and Vader and the others to a lesser degree.

### Question

Is there a similar distribution of line length between characters? Are some more prone to long lines than others?


```{r imports}
# Importing Scripts
ep.iv <- import("C:/Programming Projects/R-Practice/SW_EpisodeIV.txt")
ep.v <- import("C:/Programming Projects/R-Practice/SW_EpisodeV.txt")
ep.vi <- import("C:/Programming Projects/R-Practice/SW_EpisodeVI.txt")

# Initializing Variables
luke.iv <- (nchar(ep.iv$dialogue[ep.iv$character == "LUKE"]))
luke.v <- (nchar(ep.v$dialogue[ep.v$character == "LUKE"]))
luke.vi <- (nchar(ep.vi$dialogue[ep.vi$character == "LUKE"]))
luke.all <- c(luke.iv, luke.v, luke.vi)


vader.iv <- (nchar(ep.iv$dialogue[ep.iv$character == "VADER"]))
vader.v <- (nchar(ep.v$dialogue[ep.v$character == "VADER"]))
vader.vi <- (nchar(ep.vi$dialogue[ep.vi$character == "VADER"]))
vader.all <- c(vader.iv, vader.v, vader.vi)

```

## All Luke Lines
```{r, echo = FALSE}
show(luke.all)
```

## All Vader Lines
```{r, echo = FALSE}
show(vader.all)
```


```
## Including Plots
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
character <- luke.iv

hist(character, main = "Length of Luke and Vader's Lines: Episode IV", 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 600), ylim = c(0, 200), breaks = 8,
     col = "#2E67F8", border = "#4A7DFF")

     
character2 <- vader.iv

hist(character2, 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 300), ylim = c(0, 200), breaks = 8,
     col = "#EB212E", border = "#9E0B15",
     add = TRUE)
abline(v = median(c(character, character2)),                       # Add line for median
       col = "black",
       lwd = 3)
text(x = median(c(character, character2)) + 120,                   # Add text for median
     y = 180,
     paste("median =", round(median(character2), 2)),
     col = "black",
     cex = 1.5)
     
legend('topright', c('Vader', 'Luke'), fill=c('#EB212E', '#2E67F8'))
```


```{r}
character <- luke.v

hist(character, main = "Length of Luke and Vader's Lines: Episode V", 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 600), ylim = c(0, 200), breaks = 8,
     col = "#2E67F8", border = "#4A7DFF")

     
character2 <- vader.v

hist(character2, 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 300), ylim = c(0, 200), breaks = 8,
     col = "#EB212E", border = "#9E0B15",
     add = TRUE)
abline(v = median(c(character, character2)),                       # Add line for median
       col = "black",
       lwd = 3)
text(x = median(c(character, character2)) + 120,                   # Add text for median
     y = 180,
     paste("median =", round(median(character2), 2)),
     col = "black",
     cex = 1.5)
     
legend('topright', c('Vader', 'Luke'), fill=c('#EB212E', '#2E67F8'))
```


```{r}
character <- luke.vi

hist(character, main = "Length of Luke and Vader's Lines: Episode VI", 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 600), ylim = c(0, 200), breaks = 8,
     col = "#2E67F8", border = "#4A7DFF")

     
character2 <- vader.vi

hist(character2, 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 300), ylim = c(0, 200), breaks = 8,
     col = "#EB212E", border = "#9E0B15",
     add = TRUE)
abline(v = median(c(character, character2)),                       # Add line for median
       col = "black",
       lwd = 3)
text(x = median(c(character, character2)) + 120,                   # Add text for median
     y = 180,
     paste("median =", round(median(character2), 2)),
     col = "black",
     cex = 1.5)
     
legend('topright', c('Vader', 'Luke'), fill=c('#EB212E', '#2E67F8'))

```
# Looking at Lukes Lines acrost all Three Films

```{r}
character <- luke.all

hist(character, main = "Length of Luke and Vader's Lines: All", 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 600), ylim = c(0, 200), breaks = 8,
     col = "#2E67F8", border = "#4A7DFF")

     
character2 <- vader.all

hist(character2, 
     xlab = "Length of Line", ylab = "Number of Lines",
     xlim = c(0, 300), ylim = c(0, 200), breaks = 8,
     col = "#EB212E", border = "#9E0B15",
     add = TRUE)
abline(v = median(c(character, character2)),                       # Add line for median
       col = "black",
       lwd = 3)
text(x = median(c(character, character2)) + 120,                   # Add text for median
     y = 180,
     paste("median =", round(median(character2), 2)),
     col = "black",
     cex = 1.5)
     
legend('topright', c('Vader', 'Luke'), fill=c('#EB212E', '#2E67F8'))


```

# CLEAN UP #################################################

### Clear environment
rm(list = ls()) 

### Clear packages
detach("package:datasets", unload = TRUE)  # For base

### Clear plots
dev.off()  # But only if there IS a plot

### Clear console
cat("\014")  # ctrl+L

### Clear mind :)

